ms_0_intro

### 2018-02-07 man/ms_0_intro.Rmd
update biblio

In the Iberian Peninsula, major drought episodies were recorded in 1981, 1995, 2000 and 2005 [@VicenteSerrano2014]. The 2004/2005 and 2011/2012 hydrological years are considered two of the worst drought periods recorded in the Iberian Peninsula, particularly in the southern sector [@GarciaHerrera2007; @Gouveia2015; @Trigo2013]. These events were extreme in both its magnitude and spatial extent [@Gouveia2014].

>>>>

In the Iberian Peninsula, major drought episodies were recorded in 1981, 1995, 2000 and 2005 [@VicenteSerrano2014]. The 2004/2005 and 2011/2012 hydrological years are considered two of the worst drought periods recorded in the Iberian Peninsula, particularly in the southern sector [@GarciaHerrera2007; @Gouveia2015; @Trigo2013; @Pascoa2017]. These events were extreme in both its magnitude and spatial extent [@Gouveia2014].
